Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation

### 2024-12-14 paper/paper.qmd
Add files via upload

---
title: "Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation"
subtitle: “Assessing the Impact of Tram Prioritization on Urban Traffic Efficiency”
author: 
  - Irene Liu
thanks: "Code and data are available at: [https://github.com/zilin1017/King-Street-Traffic-Pilot-Project](https://github.com/zilin1017/King-Street-Traffic-Pilot-Project)."
date: today
date-format: long
abstract: "The paper provides a detailed analysis of the King Street transport pilot project, which aims to assess the impact of prioritizing trams over private cars on transport reliability, speed and capacity. Through the modeling and improvement of traffic data, the study gradually optimized the model variables and found that the model after logarithmic transformation performed best, with R-Square = 0.6345, which significantly improved the explanatory power of traffic flow changes. The pilot policy has achieved significant results in reducing traffic pressure at specific intersections and reducing interference from private cars. The effect of the policy is particularly significant on road sections with heavy traffic and during peak hours. In addition, the impact of different time periods and intersection characteristics on traffic patterns shows complex dynamic characteristics, which further indicates that targeted adjustment of traffic signals and optimization of priority policy implementation strategies will help further improve policy effects."
format: pdf
number-sections: true
bibliography: references.bib
citeproc: true
---
# Introduction

@@

This survey data is titled About King St. Transit Pilot - Traffic & Pedestrian Volumes Summary[@torontoKingSt] and is available on Open Data Toronto at [https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/](https://open.toronto.ca/dataset/king-st-transit-pilot-traffic-pedestrian-volumes-summary/). It can be downloaded programmatically via the API, with example `R` code provided in the file "00-download_data.R".This dataset pertains to the King Street Transit Pilot, which commenced on November 12, 2017[@toronto_transit_data_2017,@toronto_king_street_proposal_2017a], and was implemented along King Street between Bathurst Street and Jarvis Street. The pilot aimed to prioritize streetcar traffic over private vehicles to improve transit reliability, speed, and capacity. The dataset provides monthly updates on traffic and pedestrian volumes recorded within the pilot area throughout the project, offering valuable data for analyzing the impacts of this transit initiative. It serves as a critical resource for evaluating the effectiveness of the pilot in optimizing urban transit and informing future city planning and transportation policies.

@@

After introducing the source and background of the data, here we will explain how to use the `R` language [@citeR] functions and some additional packages learned in the course to process the data. Here is a unified overview. The `dplyr` package [@dplyr] is a grammar of data manipulation, providing a consistent set of verbs that help us solve the most common data manipulation challenges. In this package, this article mainly uses the `mutate` function and the `filter`function, where the `mutate`[@dplyrMutate] function creates new columns that are functions of existing variables. The `filter` [@dplyrFilter] function is used to subset a data frame, retaining all rows that satisfy conditions.In the visualization stage, this article uses the `ggplot2`[@ggplot2] package to draw graphics, and when analyzing the results, in order to see the output results more intuitively, this article also uses the `xtable`[@xtable] package to convert the results into `LaTex` format for output. Finally, in order to output the variable data that needs to be analyzed, this article also draws on the `arrow`[@arrow] package recommended in the course to output data in `parquet` format, and other Key libraries that supported the data analysis include `readxl`[@readxl], ggbeeswarm`[@ggbeeswarm], `tidyverse`[@tidyverse], `patch`[@patch], `bayesplot`[@bayesplot], `rstanarm`[@rstanarm]. Also this analysis inherits the folder structure from Professor Rohan Alexander from University of Toronto [@Rohan].

@@

@@

\begin{table}[h!]
\centering
\begin{tabular}{lp{10cm}}
\toprule
\textbf{Variable Name} & \textbf{Description} \\ 
\midrule
\texttt{aggregation\_period} & Month or baseline period for the data collection. Represents the time frame of aggregated counts. \\
\texttt{int\_id} & Unique identifier for each intersection. Can be linked to the intersection geometry dataset. \\ 
\texttt{intersection\_name} & Name of the intersection where data was collected. \\ 
\texttt{px} & Traffic signal ID, which can be joined to the traffic signal dataset for additional details. \\ 
\texttt{classification} & Category of observed traffic users. Differentiates between pedestrians, vehicles, and cyclists. \\ 
\texttt{dir} & Direction of travel at the intersection, including Northbound (\texttt{NB}), Southbound (\texttt{SB}), Eastbound (\texttt{EB}), and Westbound (\texttt{WB}). \\ 
\texttt{period\_name} & The time period during which data was collected. \\ 
\texttt{volume} & Observed count of users (vehicles, bicycles, or pedestrians) during the specified period. \\ 
\bottomrule
\end{tabular}
\caption{Variable descriptions for the King Street Transit Pilot dataset.}
\label{table:variables}
\end{table}

>>>>

---
title: "Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation"
subtitle: “Assessing the Impact of Tram Prioritization on Urban Traffic Efficiency”
author: 
  - Irene Liu
thanks: "Code and data are available at: [https://github.com/zilin1017/King-Street-Traffic-Pilot-Project](https://github.com/zilin1017/King-Street-Traffic-Pilot-Project)."
date: today
date-format: long
abstract: "The paper provides a detailed analysis of the King Street transport pilot project, which aims to assess the impact of prioritizing trams over private cars on transport reliability, speed and capacity. Through the modeling and improvement of traffic data, the study gradually optimized the model variables and found that the model after logarithmic transformation performed best, with R-Square = 0.6345, which significantly improved the explanatory power of traffic flow changes. The pilot policy has achieved significant results in reducing traffic pressure at specific intersections and reducing interference from private cars. The effect of the policy is particularly significant on road sections with heavy traffic and during peak hours. In addition, the impact of different time periods and intersection characteristics on traffic patterns shows complex dynamic characteristics, which further indicates that targeted adjustment of traffic signals and optimization of priority policy implementation strategies will help further improve policy effects."
format:
  pdf:
    number-sections: true
    table-caption: true
number-sections: true
bibliography: references.bib
citeproc: true
---
# Introduction

@@

This survey data is titled About King St. Transit Pilot - Traffic & Pedestrian Volumes Summary and is available on Open Data Toronto[@torontoKingSt]. It can be downloaded programmatically via the API, with example `R` code provided in the file "00-download_data.R".This dataset pertains to the King Street Transit Pilot, which commenced on November 12, 2017[@toronto_transit_data_2017,@toronto_king_street_proposal_2017a], and was implemented along King Street between Bathurst Street and Jarvis Street. The pilot aimed to prioritize streetcar traffic over private vehicles to improve transit reliability, speed, and capacity. The dataset provides monthly updates on traffic and pedestrian volumes recorded within the pilot area throughout the project, offering valuable data for analyzing the impacts of this transit initiative. It serves as a critical resource for evaluating the effectiveness of the pilot in optimizing urban transit and informing future city planning and transportation policies.

@@

After introducing the source and background of the data, here we will explain how to use the `R` language [@citeR] functions and some additional packages learned in the course to process the data. Here is a unified overview. The `dplyr` package [@dplyr] is a grammar of data manipulation, providing a consistent set of verbs that help us solve the most common data manipulation challenges. In this package, this article mainly uses the `mutate` function and the `filter`function, where the `mutate`[@dplyrMutate] function creates new columns that are functions of existing variables. The `filter` [@dplyrFilter] function is used to subset a data frame, retaining all rows that satisfy conditions.In the visualization stage, this article uses the `ggplot2`[@ggplot2] package to draw graphics, and when analyzing the results, in order to see the output results more intuitively, this article also uses the `xtable`[@xtable] package to convert the results into `LaTex` format for output. Finally, in order to output the variable data that needs to be analyzed, this article also draws on the `arrow`[@arrow] package recommended in the course to output data in `parquet` format, and other Key libraries that supported the data analysis include `readxl`[@readxl], `ggbeeswarm` [@ggbeeswarm], `tidyverse`[@tidyverse], `patch`[@patch], `bayesplot`[@bayesplot], `rstanarm`[@rstanarm]. Also this analysis inherits the folder structure from Professor Rohan Alexander from University of Toronto [@Rohan].

@@

\begin{table}[h!]
\centering
\begin{tabular}{lp{10cm}}
\toprule
\textbf{Variable Name} & \textbf{Description} \\ 
\midrule
\texttt{aggregation\_period} & Month or baseline period for the data collection. Represents the time frame of aggregated counts. \\
\texttt{int\_id} & Unique identifier for each intersection. Can be linked to the intersection geometry dataset. \\ 
\texttt{intersection\_name} & Name of the intersection where data was collected. \\ 
\texttt{px} & Traffic signal ID, which can be joined to the traffic signal dataset for additional details. \\ 
\texttt{classification} & Category of observed traffic users. Differentiates between pedestrians, vehicles, and cyclists. \\ 
\texttt{dir} & Direction of travel at the intersection, including Northbound (\texttt{NB}), Southbound (\texttt{SB}), Eastbound (\texttt{EB}), and Westbound (\texttt{WB}). \\ 
\texttt{period\_name} & The time period during which data was collected. \\ 
\texttt{volume} & Observed count of users (vehicles, bicycles, or pedestrians) during the specified period. \\ 
\bottomrule
\end{tabular}
\caption{Variable descriptions for the King Street Transit Pilot dataset.}
\label{table:variable}
\end{table}

@@
